---
title: 'Objective 1: Healthcare utilisation 2019 to 2022'
author: "SLICK"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: html_document
---

# Disclosure controls

* All tabulated counts are rounded to the nearest 10 (0 counts retained).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, 
                      warning=FALSE)

# Load packages ----
library(tidyverse)
library(lubridate)
library(finalfit)
library(scales)
library(zoo)
library(knitr)

# Load custom functions and lookup tables ----
source(here::here("analysis", "00_utility_functions.R"))
source(here::here("analysis", "00_lookup_tables.R"))

# Plot theme
theme_set(theme_bw())

```

```{r global_variables}

# Load global variables ----
global_var = jsonlite::read_json(path = here::here("analysis", "global_variables.json"))

## Study dates ----
study_start_date = ymd(global_var$start_date)
study_end_date   = ymd(global_var$end_date)
tp_start_date    = ymd(global_var$tp_start_date)
tp_end_date      = ymd(global_var$tp_end_date)
fup_start_date   = ymd(global_var$fup_start_date)

```


```{r load_data}

# Load datasets
data_patient = read_rds(here::here("output", "data", "data_patient.rds"))
data_testing = read_rds(here::here("output", "data", "data_testing.rds"))
data_admissions = read_rds(here::here("output", "data", "data_admissions.rds"))
data_outpatient = read_rds(here::here("output", "data", "data_outpatient.rds"))
data_gp = read_rds(here::here("output", "data", "data_gp.rds"))

```


```{r cohort_construction}

index_date = c("2019-01-01",
               "2020-01-01",
               "2021-01-01",
               "2022-01-01") %>% 
  ymd() %>% 
  as.list()

data_criteria = map(.x = index_date,
    .data_patient = data_patient,
    .f = function(.index_date, .data_patient){
      data_criteria = .data_patient %>% 
        transmute(
          patient_id,
          index_date = .index_date,
          cohort = year(index_date),
          age_indexed = time_length(
            interval(date_of_birth, .index_date),
            unit = "years"
          ) %>% 
            ff_label("Age on 1st January (years)"),
          age_group_indexed = age_indexed %>%
            cut(
              breaks = c(-Inf, 4, 7, 11, 15, 18, Inf),
              labels = c("Under 4", "4-6", "7-10", "11-14", "15-17", "18+")
            )%>%
            ff_label("Age group on 1st January (years)"),
          is_alive = is.na(death_date) | death_date > index_date, 
          isnot_nosocomial = covid_nosocomial == "No",
          isnot_descrepant_result = covid_discrepant_test == "No",
          is_age_4_or_more = age_indexed >= 4,
          is_age_under_18 = age_indexed < 18,
          include = is_alive & 
            isnot_nosocomial & 
            isnot_descrepant_result &
            is_age_4_or_more & is_age_under_18
        )
    }
  )

data_cohort = data_criteria %>% 
  map(
    function(.data_criteria){
      data_cohort = .data_criteria %>%
        filter(include) %>%
        select(patient_id, cohort, index_date, age_indexed, age_group_indexed) %>% 
        left_join(
          data_patient, by = "patient_id"
        )
    }
  )

```

# Cohorts

## Inclusion flowchart

```{r inclusion_flowchart}

flowchart = data_criteria %>% 
  map(
    function(.data_criteria){
      ## Create inclusion flowchart ----
      flowchart = .data_criteria %>%
        transmute(
          patient_id,
          cohort,
          c0 = TRUE,
          c1 = c0 & isnot_nosocomial,
          c2 = c1 & isnot_descrepant_result,
          c3 = c2 & is_alive,
          c4 = c3 & (is_age_4_or_more & is_age_under_18),
        ) %>%
        select(-patient_id) %>%
        group_by(cohort) %>%
        summarise(
          across(.fns=sum)
        ) %>%
        pivot_longer(
          cols=-cohort,
          names_to="criteria",
          values_to="n"
        ) %>%
        group_by(cohort) %>%
        mutate(
          n = n %>% plyr::round_any(10)
        ) %>% 
        mutate(
          n_exclude = lag(n) - n,
          pct_all = (n/first(n)) %>% percent(0.1),
          pct_exclude_step = (n_exclude/lag(n)) %>% percent(0.1),
          crit = str_extract(criteria, "^c\\d+"),
          criteria = fct_case_when(
            crit == "c0" ~ "OpenSAFELY extract: Registered with GP, alive, with age >1 and <18 years on 01 January 2019",
            crit == "c1" ~ "-  with no probable nosocomial infection",
            crit == "c2" ~ "-  with no same-day discrepent RT-PCR test result",
            crit == "c3" ~ "-  is alive on 1st January",
            crit == "c4" ~ "-  with age between 4 and 17 years inclusive",
            TRUE ~ NA_character_
          )
        ) %>%
        mutate(n_exclude = n_exclude %>% as.character()) %>% 
        replace_na(
          list(n_exclude = "-", pct_exclude_step = "-")
        )
    }
  ) %>% 
  bind_rows()

flowchart %>% 
  select(cohort, criteria, n, n_exclude, pct_all, pct_exclude_step) %>%
  group_by(cohort) %>% 
  mutate(cohort = if_else(row_number() == 1, cohort %>% as.character(), "")) %>% 
  kable(
    col.names = c("Cohort", "Criteria", "Count (n)", 
                  "Excluded (n)", "% of extract", "% excluded (step)"),
    align = c("l", "l", "r", "r", "r","r")
  )


```

## Patient summary

```{r}


explanatory_var = c(
  "age_indexed",
  "age_group_indexed",
  "sex",
  "ethnicity",
  "imd_Q5_2019",
  "region_2019",
  "rural_urban_2019",
  
  "covid_status_fup",
  "covid_test_neg_tp_count",
  "covid_test_pos_tp_count",
  "covid_test_neg_fup_count",
  "covid_test_pos_fup_count",
  
  "asthma",
  "cancer",
  "diabetes",
  "epilepsy",
  "severe_mental_illness",
  
  "cerebral_palsy",
  "chronic_infections",
  "devices_and_stomas",
  "endocrine_disorders",
  "gastrointestinal_disorders",
  "haematological_disorders",
  "immunological_disorders", 
  "learning_and_behaviour_difficulties", 
  "mental_illness",
  "musculoskeletal_and_rheum",
  "transplant"
)

data_cohort %>% 
  map(
    .explanatory_var = explanatory_var,
    .f = function(.data_cohort, .explanatory_var){
      .data_cohort %>%
        mutate(cohort = cohort %>% factor()) %>% 
        summary_factorlist(
          dependent = "cohort",
          explanatory = .explanatory_var,
          total_col = FALSE,
          add_col_totals = TRUE,
          na_include = TRUE
          
        ) %>% 
        mutate(row_num = row_number())
    }) %>% 
  reduce(left_join, by = c("row_num", "label", "levels")) %>% 
  select(-row_num) %>% 
  ff_round_counts() %>% 
  kable(align = c("l", "r", "r", "r", "r", "r"))





```


```{r count_monthly_admission}


boot_admissions = function(.data_patient, .data_admissions,
                           start_date, end_date, unit = "month",
                           .group = NULL, B = 10){
  
  periods = seq(start_date, end_date, by = unit)
  
  admission_counts = .data_admissions %>%
      rowwise() %>% 
      mutate(dates = list(seq(admission_date, discharge_date, by = "day"))) %>% 
      unnest(dates) %>% 
      mutate(date_period = floor_date(dates, unit = unit)) %>% 
      count(patient_id, date_period)
  
    map_df(
      .x = periods,
      .data_patient = .data_patient,
      .admission_counts = admission_counts,
      B = B, .group = .group,
      .f = function(.x, .data_patient, .admission_counts, B, .group){
        .data_patient %>%
          select(patient_id, all_of(.group)) %>% 
          mutate(
            date_period = .x,
          ) %>% 
          left_join(
            .admission_counts,
            by = c("patient_id", "date_period")
          ) %>% 
          replace_na(list(n = 0)) %>%
          group_by(across(all_of(.group))) %>% 
          summarise(
            date = .x,
            n_count = n(),
            x_boot = list(Hmisc::smean.cl.boot(n, B = B))
          ) %>% 
          unnest_wider(x_boot)
      }
    )
}

boot_outpatient = function(.data_patient, .data_outpatient,
                           start_date, end_date, unit = "month",
                           .group = NULL, B = 10){
  
  periods = seq(start_date, end_date, by = unit)
  
  outpatient_counts = .data_outpatient %>% 
      mutate(date_period = floor_date(outpatient_date, unit = unit)) %>% 
      count(patient_id, date_period)
  
    map_df(
      .x = periods,
      .data_patient = .data_patient,
      .outpatient_counts = outpatient_counts,
      B = B, .group = .group,
      .f = function(.x, .data_patient, .outpatient_counts, B, .group){
        .data_patient %>%
          select(patient_id, all_of(.group)) %>% 
          mutate(
            date_period = .x,
          ) %>% 
          left_join(
            .outpatient_counts,
            by = c("patient_id", "date_period")
          ) %>% 
          replace_na(list(n = 0)) %>%
          group_by(across(all_of(.group))) %>% 
          summarise(
            date = .x,
            n_count = n(),
            x_boot = list(Hmisc::smean.cl.boot(n, B = B))
          ) %>% 
          unnest_wider(x_boot)
      }
    )
}

boot_gp = function(.data_patient, .data_gp,
                           start_date, end_date, unit = "month",
                           .group = NULL, B = 10){
  
  periods = seq(start_date, end_date, by = unit)
  
  gp_counts = .data_gp %>% 
      mutate(date_period = floor_date(gp_date, unit = unit)) %>% 
      count(patient_id, date_period)
  
    map_df(
      .x = periods,
      .data_patient = .data_patient,
      .gp_counts = gp_counts,
      B = B, .group = .group,
      .f = function(.x, .data_patient, .gp_counts, B, .group){
        .data_patient %>%
          select(patient_id, all_of(.group)) %>% 
          mutate(
            date_period = .x,
          ) %>% 
          left_join(
            .gp_counts,
            by = c("patient_id", "date_period")
          ) %>% 
          replace_na(list(n = 0)) %>%
          group_by(across(all_of(.group))) %>% 
          summarise(
            date = .x,
            n_count = n(),
            x_boot = list(Hmisc::smean.cl.boot(n, B = B))
          ) %>% 
          unnest_wider(x_boot)
      }
    )
}

plot_admissions = function(.index_date, .data_cohort, 
                           .data_admissions, .group = NULL,
                           group_lab = NULL){
  if(is.null(.group)){
    group_lab = NULL
  } else if (is.null(group_lab)) {
    group_lab = extract_variable_label(
      .data_cohort[[1]])[.group]
  }
  
  plot_data = map2(
    .x = .index_date,
    .y = .data_cohort,
    .data_admissions = .data_admissions,
    .group = .group,
    .f = function(.x, .y, .data_admissions, .group = .group){
      boot_admissions(
        start_date = .x,
        end_date = min(ceiling_date(.x, "year") - days(1), study_end_date) - days(1),
        unit = "month",
        .group = .group,
        .data_patient = .y,
        .data_admissions = .data_admissions
      )
    }
  ) %>% 
    bind_rows()
  
  plot_data %>%
    mutate(date = date + days(14)) %>% 
    ggplot(aes_string("date", "Mean", colour = .group, fill = .group)) +
    geom_line() + geom_point(size = 1) +
    geom_ribbon(aes(ymin = Lower, ymax = Upper), alpha = 0.1, linetype = "dashed", size = 0.2) +
    labs(
      y = "Mean bed-days per month per patient",
      x = NULL, colour = group_lab, fill = group_lab
    ) +
    theme(
      legend.position = "bottom"
    )
}

plot_outpatient = function(.index_date, .data_cohort, 
                           .data_outpatient, .group = NULL,
                           group_lab = NULL){
  if(is.null(.group)){
    group_lab = NULL
  } else if (is.null(group_lab)) {
    group_lab = extract_variable_label(
      .data_cohort[[1]])[.group]
  }
  
  plot_data = map2(
    .x = .index_date,
    .y = .data_cohort,
    .data_outpatient = .data_outpatient,
    .group = .group,
    .f = function(.x, .y, .data_outpatient, .group = .group){
      boot_outpatient(
        start_date = .x,
        end_date = min(ceiling_date(.x, "year") - days(1), study_end_date) - days(1),
        unit = "month",
        .group = .group,
        .data_patient = .y,
        .data_outpatient = .data_outpatient
      )
    }
  ) %>% 
    bind_rows()
  
  plot_data %>%
    mutate(date = date + days(14)) %>% 
    ggplot(aes_string("date", "Mean", colour = .group, fill = .group)) +
    geom_line() + geom_point(size = 1) +
    geom_ribbon(aes(ymin = Lower, ymax = Upper), alpha = 0.1, linetype = "dashed", size = 0.2) +
    labs(
      y = "Mean outpatient contact (days per month per patient)",
      x = NULL, colour = group_lab, fill = group_lab
    ) +
    theme(
      legend.position = "bottom"
    )
}

plot_gp = function(.index_date, .data_cohort, 
                   .data_gp, .group = NULL,
                   group_lab = NULL){
  
  if(is.null(.group)){
    group_lab = NULL
  } else if (is.null(group_lab)) {
    group_lab = extract_variable_label(
      .data_cohort[[1]])[.group]
  }
  
  plot_data = map2(
    .x = .index_date,
    .y = .data_cohort,
    .data_gp = .data_gp,
    .group = .group,
    .f = function(.x, .y, .data_gp, .group = .group){
      boot_gp(
        start_date = .x,
        end_date = min(ceiling_date(.x, "year") - days(1), study_end_date) - days(1),
        unit = "month",
        .group = .group,
        .data_patient = .y,
        .data_gp = .data_gp
      )
    }
  ) %>% 
    bind_rows()
  
  plot_data %>%
    mutate(date = date + days(14)) %>% 
    ggplot(aes_string("date", "Mean", colour = .group, fill = .group)) +
    geom_line() + geom_point(size = 1) +
    geom_ribbon(aes(ymin = Lower, ymax = Upper), alpha = 0.1, linetype = "dashed", size = 0.2) +
    labs(
      y = "Mean healthcare contact (days per month per patient)",
      x = NULL, colour = group_lab, fill = group_lab
    ) +
    theme(
      legend.position = "bottom"
    )
}

```

# Healthcare resource use

## Overall {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = NULL)
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = NULL)
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = NULL)
```


## Covid status {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "covid_status_tp")
```

### Outpatient

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "covid_status_tp")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "covid_status_tp")
```


## Age group  {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "age_group_indexed")
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "age_group_indexed")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "age_group_indexed")
```


## Sex {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "sex")
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient =  data_outpatient,
                .group = "sex")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "sex")
```


## Ethnicity {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "ethnicity")
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "ethnicity")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "ethnicity")
```


## IMD {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "imd_Q5_2019")
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "imd_Q5_2019")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "imd_Q5_2019")
```


## Region {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "region_2019")
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "region_2019")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "region_2019")
```


## Asthma {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "asthma")
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "asthma")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "asthma")
```


## Cancer {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "cancer")
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "cancer")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "cancer")
```


## Epilepsy {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "epilepsy")
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "epilepsy")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "epilepsy")
```


## Mental illness {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "mental_illness")
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "mental_illness")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "mental_illness")
```


## Severe mental illness {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "severe_mental_illness")
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "severe_mental_illness")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "severe_mental_illness")
```


## Cerebral palsy {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "cerebral_palsy")
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "cerebral_palsy")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "cerebral_palsy")
```


## Chronic infections {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "chronic_infections")
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "chronic_infections")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "chronic_infections")
```


## Devices and stomas {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "devices_and_stomas")
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "devices_and_stomas")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "devices_and_stomas")
```


## Endocrine disorders {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "endocrine_disorders")
```

### Outpatient

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "endocrine_disorders")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "endocrine_disorders")
```


## Gastrointestinal disorders {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "gastrointestinal_disorders")
```

### Outpatient

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "gastrointestinal_disorders")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "gastrointestinal_disorders")
```


## Haematological disorders {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "haematological_disorders")
```

### Outpatient

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "haematological_disorders")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "haematological_disorders")
```


## Immunological disorders {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "immunological_disorders")
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "immunological_disorders")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "immunological_disorders")
```


## Learning and behaviour difficulties {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "learning_and_behaviour_difficulties")
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "learning_and_behaviour_difficulties")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "learning_and_behaviour_difficulties")
```


## Musculoskeletal and rheumatic diseases {.tabset}

### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "musculoskeletal_and_rheum")
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "musculoskeletal_and_rheum")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "musculoskeletal_and_rheum")
```


## Transplant {.tabset}


### Admissions

```{r}
plot_admissions(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_admissions = data_admissions,
                .group = "transplant")
```

### Outpatient 

```{r}
plot_outpatient(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_outpatient = data_outpatient,
                .group = "transplant")
```

### GP records

```{r}
plot_gp(.index_date = index_date, 
                .data_cohort = data_cohort, 
                .data_gp = data_gp,
                .group = "transplant")
```

